Approximate Code: A Cost-Effective Erasure Coding Framework for Video Applications in Cloud Storage Systems

### 2019-04-17 ApproximateCode.tex
version 3.6.4

\begin{table}[ht]
\centering 
\caption{Comparison of fault tolerance and storage overhead between approximate storage, EC and Approximate Code}\label{tab-AS-EC-AP}
\begin{tabular}{|c|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{Schemes}  & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & Realibilities & Performance \\ \hline\hline
\multirow{2}{*}{EC} & RS & high & high & medium \\ \cline{2-5} 
\multicolumn{1}{|c|}{} & RAID 6 & medium & medium & high \\ \hline
\multicolumn{2}{|c|}{Ap-Storage}& low & low & high \\ \hline
\multirow{2}{*}{Ap-Code}& Imp & \multirow{2}{*}{low} & high & high \\ \cline{2-2} \cline{4-5} 
 & unimportant &  & medium & high \\ \hline
\end{tabular}
\end{table}

@@

The construction of the Approximate Code is determined by 3 parameters $k$, $r$ and $h$. 
First, we use Figure \ref{fig-chunk-block} to illustrate the term \emph{chunk}, \emph{block} and \emph{stripe} we use in this paper. In a $n$-node system, $k$ of them are data nodes and $r=n-k$ nodes are for parity. Each node can be divided into multiple blocks. We focus on the $s$ blocks of the same logical position of each node, and we treat these $s$ nodes as a \emph{chunk}. The $n$ chunks constitute a \emph{stripe}. 
Approximate Code are designed for $h$ stripes, where each stripe is in the same $n$-node system.
%Approximate Code are designed for $h$ stripes, where each stripe can be in the same $n$-node system, or on different $n$-node systems.
%We define the former situation as \emph{Situation I}, which we pay more attantion on, while the latter is defined as \emph{Situation II}.

@@

\subsubsection{Reconstruction cases in Structure 1}
Under \emph{Structure 1}, important data and unimportant data are distributed in

\subsubsection{Reconstruction cases in Structure 2}

>>>>

\begin{table}[ht]
\centering 
\caption{Comparison of fault tolerance and storage overhead between approximate storage, EC and Approximate Code}\label{tab-AS-EC-AP}
\begin{tabular}{|c|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{Schemes}  & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & Realibilities & Performance \\ \hline\hline
\multirow{2}{*}{EC} & RS & high & high & medium \\ \cline{2-5} 
\multicolumn{1}{|c|}{} & RAID 6 & medium & medium & high \\ \hline
\multicolumn{2}{|c|}{Ap-Storage}& low & low & high \\ \hline
\multirow{2}{*}{Ap-Code}& Imp & \multirow{2}{*}{low} & high & high \\ \cline{2-2} \cline{4-5} 
 & Unimp &  & medium & high \\ \hline
\end{tabular}
\end{table}

@@

The construction of the Approximate Code is determined by 3 parameters $k$, $r$ and $h$. 
First, we use Figure \ref{fig-chunk-block} to illustrate the term \emph{chunk}, \emph{block} and \emph{stripe} we use in this paper. In a $n$-node system, $k$ of them are data nodes and $r=n-k$ nodes are for parity. Each node can be divided into multiple blocks. We focus on the $s$ blocks of the same logical position of each node, and we treat these $s$ nodes as a \emph{chunk}. The $n$ chunks constitute a \emph{stripe}. 
%Approximate Code are designed for $h$ stripes, where each stripe is in the same $n$-node system.
Approximate Code are designed for $h$ stripes, where each stripe can be in the same $n$-node system, or in different $n$-node systems.
%We define the former situation as \emph{Situation I}, which we pay more attantion on, while the latter is defined as \emph{Situation II}.

@@

\subsubsection{Reconstruction cases in Structure 1}
Under \emph{Structure 1}, important data and unimportant data are distributed in the same chunks, so they suffer the same risk of device failures. 
When $r$ or less nodes fail, all the data can be reconstructed by local parity.
When the number of failed nodes is over $r$ but no more than 3, the Approximate Code conduct approximate recovery, where the important data are recovered by global parity chunks and the damaged video data will be processed by the video recovery and fuzzy algorithm.

\subsubsection{Reconstruction cases in Structure 2}
Under \emph{Structure 2}, we consider important and unimportant data chunks separately.
